---
title: "p8105_hw1_ks3663"
author: "Kee-Young Shin"
date: "September 13, 2018"
output: html_document
---
## Problem 1

```{r}
set.seed(1)

random_sample = runif(10, 0, 5) 
vec_logic = random_sample > 2
vec_char = as.character(vec_logic) # created character vector by coercing vec_logic
vec_factor = as.factor(vec_logic)  # created factor vector by coercing vec_logic

pr1_df = data.frame(random_sample, vec_logic, vec_char, vec_factor, stringsAsFactors = FALSE)

mean(pr1_df$random_sample) # taking the mean of each variable in the data frame 
mean(pr1_df$vec_logic)
mean(pr1_df$vec_char) 
mean(pr1_df$vec_factor) 

```
The means of the random sample vector and logical vector are able to be calculated since there are real numbers in the vectors (True and False are assigned values 1 and 0). On the other hand, the means of the character vector and factor vector cannot be calculated because there are no numbers assigned to those vectors. 


```{r }

as.numeric(pr1_df$vec_logic) #converts to values of 1 and 0
as.numeric(pr1_df$vec_char) #converts to a vector full of NA since there is no number
as.numeric(pr1_df$vec_factor) #saying first element is level 2 

```
The logic vector is able to be turned into a numeric vector since True and False can be converted to 1 and 0, respectively, in R. The factor vector is able to be converted into a numeric vector related to the levels of the values in it. The character vector is turned into a vector full of NA's since a character does not have an associated number.


```{r}
as.numeric(as.factor(pr1_df$vec_char)) # converting from charcter to factor to numeric

as.numeric(as.character(pr1_df$vec_factor)) # from factor to character to numeric 
```
The character vector is turned into a factor vector with two levels "FALSE" and "TRUE". The factor is then turned into a numeric vector according to the levels- 1 and 2- of the values in the factor vector. The reverse, however, does not work. Though the factor vector can be turned into a character vector, the character vector cannot be converted to a numeric vector since it is fully of characters "TRUE" and "FALSE".


## Problem 2

```{r}

x = rnorm(1000)
y = rnorm(1000)
pr2_log = (x + y) > 0
pr2_numeric = as.numeric(pr2_log)  # coerced logical vector into numeric
pr2_factor = as.factor(pr2_log)  # coerced logical vector into factor 

pr2_df = data.frame(x, y, pr2_log, pr2_numeric, pr2_factor)


```

